An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative

### 2019-06-05 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text and code

Regarding financial analysis:
\begin{itemize}
	\item LCOE lifetime considered: 20 years;
	\item Battery lifetime: 4 years for lead-acid batteries. Therefore will be performed three battery bank replacements;
	\item Installation costs: includes delivery at the isolated community and installation costs itself, 5\% of total cost~\cite{Agrener2013};
%	\item Electrical protection and complementary electrical item: 7\% of equipment cost [Agrener2013]. Includes circuit breakers, surge protection devices, electrical grounding, DC fuses, main switchboard, string boxes;
	\item Value of the discount rate or interest rate: 10\%, what is a good rate considering financial investments in developing countries;
	\item Operation and maintenance annual costs: based on past PV projects in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\citep{Agrener2013}.
\end{itemize}

@@

\begin{table}
\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{|c|c|c|c|c|}
\hline
\hline
Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)} & \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)} & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)} & HOMER Pro \\
\hline
\hline
Specification & Result & Result & Result & Result \\
\hline
\makecell{\textbf{Case Study 1}\\Demand:501W\\Peak:501W \\E:3,900Wh/day\\Autonomy:48h} & OM & IF & \makecell{SAT (146.13 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC:US\$ 1,902.60} & XYZ \\
\hline
\makecell{\textbf{Case Study 2}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:6h} & OM & IF & \makecell {SAT (105.06 min) \\NTP:3$\times$275W (3S)\\NBT:2$\times$80Ah (2S)\\Controller 30A/100V\\Inverter 1,200W/24V \\LCC:US\$ 1,323.00} & XYZ \\
\hline
\makecell{\textbf{Case Study 3}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & IF & \makecell {SAT (131.38 min) \\NTP:3$\times$330W (3S)\\NBT:2$\times$80Ah (2S)\\Controller 35A/145V\\Inverter 1,200W/24V \\LCC:US\$ 1,441.40} & XYZ \\
\hline
\makecell{\textbf{Case Study 4}\\Demand:253W\\Peak:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (145.57 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 280W/24V \\LCC:US\$ 1,927.15} & XYZ \\
\hline
\makecell{\textbf{Case Study 5}\\Demand:263W\\Peak:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (133.90 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC:US\$ 1,389.85} & XYZ \\
\hline
\makecell{\textbf{Case Study 6}\\Demand:322W\\Peak:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (234.00 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC:US\$ 2,375.65} & XYZ \\
\hline
\makecell{\textbf{Case Study 7}\\Demand:1,800W\\Peak:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & TO & TO & XYZ \\
\hline
\hline
\end{tabular}
\\Legend: OM = out of memory; TO = timeout; IF = internal failure, E = energy.
\end{scriptsize}
\end{table}

>>>>

Regarding financial analysis:
\begin{itemize}
	\item LCC lifetime considered: 20 years;
	\item Installation costs: includes delivery at the isolated community and installation costs itself, 5\% of total cost~\cite{Agrener2013};
%	\item Electrical protection and complementary electrical item: 7\% of equipment cost [Agrener2013]. Includes circuit breakers, surge protection devices, electrical grounding, DC fuses, main switchboard, string boxes;
	\item Value of the discount rate or interest rate: 10\%, what is a good rate considering financial investments in developing countries;
	\item Operation and maintenance annual costs: based on past PV projects in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\citep{Agrener2013}. This cost includes the battery lifetime (4 years for lead-acid batteries). Therefore will be performed three battery bank replacements during the LCC analysis.
\end{itemize}

@@

\begin{table}
\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{|c|c|c|c|c|}
\hline
\hline
Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)} & \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)} & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)} & HOMER Pro \\
\hline
\hline
Specification & Result & Result & Result & Result \\
\hline
\makecell{\textbf{Case Study 1}\\Demand:501W\\Peak:501W \\E:3,900Wh/day\\Autonomy:48h} & OM & IF & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC:US\$ 7,790.53} & XYZ \\
\hline
\makecell{\textbf{Case Study 2}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:6h} & OM & IF & \makecell {SAT (105.06 min) \\NTP:2$\times$320W (2S)\\NBT:2$\times$80Ah (2S)\\Controller 40A/100V DC\\Inverter 1,200W/24V \\LCC:US\$ 7,133.39} & XYZ \\
\hline
\makecell{\textbf{Case Study 3}\\Demand:915W\\Peak:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & IF & \makecell {SAT (131.38 min) \\NTP:3$\times$330W (3S)\\NBT:2$\times$80Ah (2S)\\Controller 35A/145V\\Inverter 1,200W/24V \\LCC:US\$ 1,441.40} & XYZ \\
\hline
\makecell{\textbf{Case Study 4}\\Demand:253W\\Peak:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (145.57 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 280W/24V \\LCC:US\$ 1,927.15} & XYZ \\
\hline
\makecell{\textbf{Case Study 5}\\Demand:263W\\Peak:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (133.90 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC:US\$ 1,389.85} & XYZ \\
\hline
\makecell{\textbf{Case Study 6}\\Demand:322W\\Peak:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & IF & \makecell {SAT (234.00 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC:US\$ 2,375.65} & XYZ \\
\hline
\makecell{\textbf{Case Study 7}\\Demand:1,800W\\Peak:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & TO & TO & XYZ \\
\hline
\hline
\end{tabular}
\\Legend: OM = out of memory; TO = timeout; IF = internal failure, E = energy.
\end{scriptsize}
\end{table}
